---
title: "Regularization"
author: "Rob Walker"
output: html_document
---

# Handwritten digits
- Classify pictures of numbers from 0-9

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2); library(cowplot); library(keras)
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y
use_session_with_seed(19)
x_train <- array_reshape(x_train, c(nrow(x_train), 28^2))
x_test <- array_reshape(x_test, c(nrow(x_test), 28^2))
x_train <- x_train / 255
x_test <- x_test / 255
y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)
```

# Define Keras model
- Try to overfit

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = dim(x_train)[2]) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dense(units = 64, activation = 'relu') %>%
  layer_dense(units = 10, activation = 'softmax')
model

```

# Compile the model

```{r}
model %>% compile( loss = "categorical_crossentropy", 
                   optimizer = optimizer_rmsprop(),
                   metrics = 'accuracy')

```

# Train the model
- overfitting seen in the loss

```{r, results="hide"}
history <- model %>% fit( x_train, y_train, epochs = 20, verbose = 1,
                          batch_size = 128, validation_split = 0.2)
plot(history)


```

# Train vs Test
- overfitting seen in loss

```{r}
#model %>% predict_classes(x_test)
model %>% evaluate(x_train, y_train)
model %>% evaluate(x_test, y_test)

```


# Define new Keras model
- Add regularization
- Add dropout layers

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', regularizer_l1_l2(), 
              input_shape = dim(x_train)[2]) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, regularizer_l1_l2(), activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 64, regularizer_l1_l2(), activation = 'relu') %>%
  layer_dropout(rate = 0.2) %>%
  layer_dense(units = 10, regularizer_l1_l2(), activation = 'softmax')
model

```

# Compile the model

```{r}
model %>% compile( loss = "categorical_crossentropy", 
                   optimizer = optimizer_rmsprop(),
                   metrics = 'accuracy')

```

# Train the model

```{r, results="hide"}
history <- model %>% fit( x_train, y_train, epochs = 20, verbose = 1,
                          batch_size = 128, validation_split = 0.2)
plot(history)


```

# Train vs Test

```{r}
model %>% evaluate(x_train, y_train)
model %>% evaluate(x_test, y_test)

```

# Summary
- It's easy to overfit with neural networks because they have so many weights
- 4 main weapons 1) regularization, 2) dropout, 3) stopping early, 4) tune hyperparameters (fewer neurons, fewer layers)
- Can you improve on the train and test metrics?